Case 4

### 2017-09-12 EU-Circle/eu-circle_case-study-4.Rmd
EU-Circle case study 4

Bangladesh is highly vulnerable to climate induced hazrds and disasters and its coastal part are mostly threatened for the impacts of climate change in case of cyclone, storm surges, flood, salinity and tsunami disaster. Even last twenty years the coastal peoples have suffered due to super cyclone SIDR (2007-11-15) and AILA (YYYY-MM-DD) devastations. Last two deacdes a lots of disaster coping interventions have been provided to the community to achieve resiliency in this areas. So really it will be a field laboratory for the research of Disaster Resilience and Climate Change: Science and innovation for adaptation to climate  change: from assessing costs, risks and opportunities to demonstration of options and practices.

@@

@@

>>>>

Bangladesh is highly vulnerable to climate induced hazards and disasters and its coastal part are mostly threatened for the impacts of climate change in case of cyclone, storm surges, flood, salinity and tsunami disaster. Even last twenty years the coastal peoples have suffered due to super cyclone SIDR (2007-11-15) and AILA (YYYY-MM-DD) devastations. Last two deacdes a lots of disaster coping interventions have been provided to the community to achieve resiliency in this areas. So really it will be a field laboratory for the research of Disaster Resilience and Climate Change: Science and innovation for adaptation to climate  change: from assessing costs, risks and opportunities to demonstration of options and practices.

@@

```{r}
plot(pr.bmd,new=FALSE)
```

@@

Check the annual cycle in the tidal time series. Is it caused by seasonally changing wind patterns? That would be reflected in the SLP.

```{r}
SLP <- retrieve('~/Downloads/slp.mon.mean.nc',lon=c(75,105),lat=c(5,30))
amslp <- mask(aggregate(SLP,month,FUN='mean'),land=TRUE)
eof.amslp <- EOF(amslp,n=3)
plot(eof.amslp)
```

Examine the seasonal cycle in the tidal data: extract the mean seasonal cycle using `aggregate`

```{r}
amsl <- aggregate(Z,month,'mean')
pca.amsl <- PCA(amsl,n=3)
plot(pca.amsl)
```

Use `DS` to apply a multiple regression analysis to the PCAs and EOFs describing the seasonal cycle. This is ok for short series when we know the connection is due to known physics - shifting wind patterns:

```{r, fig.height=8}
ds.asl <- DS(pca.amsl,eof.amslp,n=3)
plot(ds.asl)
```

The seasonal variations are indeed caused by seasonally shifting winth patterns. This gives an idea of the sensitivity of the local sea level to changing winds in general, as the physical forces will be similar. We cal downscale the SLP from GCMs in multi-model ensembles to try to get a robust picture. There may be some problems in the SLP simulation over the Indian sub-continent, which means that we may need to mask out the land.
